\section*{}
\begin{center}
    {\fontsize{14}{1.5}\selectfont \textbf{CHAPTER VI}}\\
    \vspace{12pt}
    {\fontsize{16}{1.5}\selectfont \textbf{Addressing Course Outcomes and Program Outcomes}}\\
    \vspace{12pt}
    \vspace{12pt}
\end{center}

\setcounter{section}{6}
\setcounter{subsection}{0}
\setcounter{table}{0}
\setcounter{figure}{0}
\addcontentsline{toc}{section}{\textbf{CHAPTER VI Addressing Course Outcomes and Program Outcomes}} % Add to ToC


\subsection{Complex Engineering Problems Associated with the Current Project}

\begin{longtable}{|p{5cm}|p{1cm}|p{8cm}|}
\caption{Range of Complex Engineering Problem Solving}
\hline
\textbf{Attribute} & \multicolumn{2}{|c|}{\textbf{Churn Prediction}} \
\hline
\textbf{Problem Analysis} & \textbf{PO2} & Might delve into the intricacies of various machine learning techniques specific to churn prediction, such as logistic regression, support vector machines, and deep learning models like recurrent neural networks. Researchers could gain an extensive understanding of these methods, exploring their effectiveness, limitations, and practical implications in predicting customer churn.
\hline
\textbf{Ethical Decision-making} & \textbf{PO8} & Involves balancing the trade-offs between model complexity and interpretability, considering factors like algorithmic transparency, fairness, and privacy concerns. Striking a balance between the predictive power of complex models and the need for transparency and fairness is crucial. Researchers must address ethical dilemmas to develop models that are both accurate and ethically sound, navigating through challenges such as algorithmic bias and data privacy.
\hline
\textbf{Individual and Teamwork Skills} & \textbf{PO9} & Encompasses optimizing churn prediction models through collaborative efforts, leveraging diverse skill sets such as data preprocessing, feature engineering, model selection, and evaluation. This involves collaboration among data scientists, domain experts, and business stakeholders to identify relevant features, experiment with different modeling techniques, and interpret model outputs effectively. The project culminates in a comprehensive analysis of model performance and actionable insights for churn mitigation strategies.
\hline
\textbf{Communication Proficiency} & \textbf{PO10} & Requires effective communication of churn prediction results and insights to various stakeholders, including business leaders, marketing teams, and customer service representatives. Researchers should be proficient in translating technical findings into actionable recommendations, conveying the importance of churn prediction in driving business strategies and customer retention efforts. Clear and concise communication is essential for ensuring alignment between data-driven insights and organizational goals.
\hline
\end{longtable}
\label{tab
}

\subsection{Complex Engineering Activities Associated with Churn Prediction}

In the realm of complex engineering activities, churn prediction entails a multifaceted approach to addressing challenges and devising innovative solutions. Table \ref{tab
} delineates critical attributes inherent in churn prediction endeavors, focusing on aspects such as resource utilization, interaction dynamics, innovation quotient, societal and environmental implications, and adeptness with relevant concepts and technologies.

\begin{longtable}{|p{5cm}|p{10cm}|}
\caption{Range of Complex Engineering Activities}
\label{tab
}

\hline
\textbf{Attribute} & \textbf{Characteristics of Churn Prediction Activities}
\hline
\textbf{Resource Spectrum} & Encompasses leveraging a diverse array of resources, including data, computational infrastructure, expertise, and domain knowledge, to effectively predict customer churn.
\hline
\textbf{Interactivity Level} & Entails addressing significant challenges arising from interactions between various factors such as customer behavior, market dynamics, and business strategies. Data scientists and business stakeholders must collaborate closely to understand churn drivers, refine predictive models, and implement targeted interventions.
\hline
\textbf{Innovative Endeavors} & Revolves around the creative application of machine learning techniques, feature engineering approaches, and model evaluation methods to develop accurate and robust churn prediction models. Researchers explore novel methodologies to uncover hidden patterns in data and enhance predictive performance, driving innovation in customer retention strategies.
\hline
\textbf{Societal and Environmental Implications} & Have profound implications for business sustainability, customer satisfaction, and market competitiveness. Effective churn prediction enables companies to allocate resources efficiently, personalize customer interactions, and minimize customer attrition, thereby contributing to economic growth and social welfare.
\hline
\textbf{Familiarity Threshold} & May extend beyond conventional approaches by leveraging advanced analytics, artificial intelligence, and big data technologies. Data scientists encounter complex challenges that demand innovative solutions, prompting them to push the boundaries of traditional analytical techniques and embrace emerging technologies to stay ahead in churn prediction. \
\hline
\end{longtable}